Finding shortest and closest vectors in a lattice of Voronoi's first kind

### 2014-04-16 talk/presentation.tex
added minor

@@

@@

\frame{
\frametitle{Lattices of Voronoi's first kind}
\begin{theorem}
Let $\Lambda$ be a $n$-dimensional lattice of Voronoi's first kind with obtuse superbase 
\[
b_1, \dots, b_{n+1}.
\]  
The short vectors in $\Lambda$ are of the form 
\[
\sum_{i \in I} b_i
\] 
where $I$ is a strict subset of $\{1, 2, \dots, n+1\}$ and $I$ is not empty.
\end{theorem}
}

@@

>>>>

\frame{
PICTURE OF VORONOI CELL
}

\frame{
\frametitle{Relevant vectors}
}

\frame{
PICTURE OF RELEVANT VECTORS
}

\frame{
\frametitle{}
}

@@

\frame{
\frametitle{The closest lattice point problem}
ADD THIS
}

@@

\frame{
\frametitle{Lattices of Voronoi's first kind}
\begin{theorem}
Let $\Lambda$ be a $n$-dimensional lattice of Voronoi's first kind with obtuse superbase $b_1, \dots, b_{n+1}$.  The relevant vectors in $\Lambda$ are of the form 
\[
\sum_{i \in I} b_i
\] 
where $I$ is a strict subset of $\{1, 2, \dots, n+1\}$ and $I$ is not empty.
\end{theorem}

\begin{corollary}
Short vectors in $\Lambda$ are of the form $\sum_{i \in I} b_i$.
\end{corollary}
}

@@

\begin{itemize}
\item Can we \sout{efficiently} decide whether a lattice is of Voronoi's first kind? {\color{red}\textbf{Yes}}
\item Can we \sout{efficiently} find an obtuse superbase if it exists? {\color{red}\textbf{Yes}}
\item Can a similar approach be taken to solve the \term{closest lattice point problem}? 
\end{itemize}
